---
title: "p8105_hw1_jt3174"
author: "Jingyi"
date: "9/16/2019"
output: html_document
---

# Problem 1

#### Create a data frame comprised of:
##### * a random sample size of 8 from a standard Normal distribution
##### * a logical vector indicating whether elements of the sample are greater than 0
##### * a character vector of length 8
##### * a factor vector of length 8, with 3 different factor “levels”

```{r Question_1_Part_1}
library(tidyverse)
set.seed(1)
# Question: Is this set.seed() here necessary?
# Question: Can I just get any character/factor vector? Or something else is required?
Part1Question1 = tibble(
  x = rnorm(8),
  y = x > 0,
  z = c("rnorm1", "rnorm2", "rnorm3", "rnorm4", "rnorm5", "rnorm6", "rnorm7", "rnorm8"),
  a = factor(c("level1", "level2","level3", "level1", "level2", "level3", "level1", "level2")))

# Question: Is this correct and am I on the right track?

# Now take the mean of each vector in the data frame.

mean_x = mean(pull(Part1Question1, x))
mean_y = mean(pull(Part1Question1, y))
mean_z = mean(pull(Part1Question1, z))
mean_a = mean(pull(Part1Question1, a))

```



```{r part1_2, results = "hide"}

# Now use the as.numeric function.
# Show the chuck but not the output.

 # Question: How do I keep both the name of the code chuck and the command together?
 # Question: What if I want to only hide the result of as.numeric part?
########################
# separate this part to hide the result but show the code chuck.

numeric_y = as.numeric(pull(Part1Question1, y)) 
numeric_z = as.numeric(pull(Part1Question1, z))
numeric_a = as.numeric(pull(Part1Question1, a))

```

For the mean value finding part:
a and y returned mean values.
For this part, the logical vector returned a mean value, it seems like R took the logical vector False as 0 and then TRUE as 1. And my calculation proves it. 
z and a did not return a mean value since z and a are not numeric.

For the as.numeric part:
All y, z and a values are converted into numeric vectors and it seemed like y and a are fine with this conversion; however, there are NA values introduced in the dataset forcefully. z failed to have true values, but NA's. If we try further with its mean, we will also get NA as output. This is because the character vector failed to convert into any numeric values. However, a converted and will also produce a mean if we try further. This is because R assigned numeric values such as 1, 2, 3's to different levels according to the order of it; hence, we can also get a mean after this forcefully transformation.
Yes, this does explain what happened when we are trying for mean function for the last part. R can't execuate mean function properly unless we have numerical values in the dataset.

#### Now Part 2 of Question 1:
##### * convert the logical vector to numeric, and multiply the random sample by the result
##### * convert the logical vector to a factor, and multiply the random sample by the result
##### * convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result


```{r}


numeric_y_1 = numeric_y * pull(Part1Question1, x)
    # Question: What do the question mean by random sample by the result?
factor_y = as.factor(pull(Part1Question1, y))

####### ATTENTION #########
factor_y_1 = factor_y * pull(Part1Question1, x)
###########################

numeric_y_2 = as.numeric(factor_y_1)
numeric_y_3 = numeric_y_2 * pull(Part1Question1, x)

```

For the factor_y part, it did not return a value, but the massage said that * is not operatable. What happened here is that the factor_y is a factor vector and this vector cannot be multiple with numeric vectors. Therefore, R cannot return any numeric values for this part of code. 

# Problem 2

#### Create a data frame comprised of:
##### * x: a random sample of size 500 from a standard Normal distribution
##### * y: a random sample of size 500 from a standard Normal distribution
##### * A logical vector indicating whether x + y > 1
##### * A numeric vector created by coercing the above logical vector
##### * A factor vector created by coercing the above logical vector

```{r}

set.seed(10)
# Question: Do I need another set.seed()?
# If I have a set.seed() here will it make x and y the same outputs?

Question2 = tibble(
  x = rnorm(500),
  y = rnorm(500),
  z = x + y > 1,
  a = as.numeric(z),
  b = as.factor(z))

# Dataframe created.

zcount = pull(Question2, z)

```

* The size of the dataset are `r nrow(Question2)` rows and `r ncol(Question2)` columns.

* The mean of x is `r mean(pull(Question2, x))`.

* The medium of x is `r median(pull(Question2, x))`.

* The standard deviation of x is `r sd(pull(Question2, x))`.

* The proportion of cases for which x + y > 1 is `r sum(zcount)/length(pull(Question2, x))`

```{r}
# Question: How do I find proportion?
# Question solved. Refer to the code above.

# When I used prop.table(table(pull(Question2, z)))
# Here the error message is :
  ### Error in table(Question2, z): object 'z' not found Calls: <Anonymous> ... withVisible -> eval -> eval -> prop.table -> pull -> table Execution halted
# However, this updated version does run, but gave me two numbers in return but this should be one only.
# WHY????
# Still wonder about prop.table()

# Scatterplot:
## Question: Does this mean y vs x? OR x vs y?
## Question Solved. 
## Question: Can I directly use x and y in this ggplot function?
ggplot(Question2, aes(x = x, y = y, color = z)) + geom_point()
ggsave("scatterplot1.jpg")

ggplot(Question2, aes(x = x, y = y, color = a)) + geom_point()
ggplot(Question2, aes(x = x, y = y, color = b)) + geom_point()

#####
# What is "color points using the logical variable (adding color = ... inside of aes in your ggplot code should help). Make a second and third scatterplot that color points using the numeric and factor variables, respectively, and comment on the color scales."
# What is "Export your first scatterplot to your project directory using ggsave."
## Question Solved.
##### 

```

