---
title: "p8105_hw1_jt3174"
author: "Jingyi"
date: "9/16/2019"
output: html_document
---

# Problem 1

#### Create a data frame comprised of:
##### * a random sample size of 8 from a standard Normal distribution
##### * a logical vector indicating whether elements of the sample are greater than 0
##### * a character vector of length 8
##### * a factor vector of length 8, with 3 different factor “levels”

```{r part_1_of_Question_1}
library(tidyverse)
set.seed(1)
# Question: Is this set.seed() here necessary?
# Question: Can I just get any character/factor vector? Or something else is required?
Part1Question1 = tibble(
  x = rnorm(8),
  y = x > 0,
  z = c("rnorm1", "rnorm2", "rnorm3", "rnorm4", "rnorm5", "rnorm6", "rnorm7", "rnorm8"),
  a = factor(c("level1", "level2","level3", "level1", "level2", "level3", "level1", "level2")))

# Question: Is this correct and am I on the right track?

# Now take the mean of each vector in the data frame.

mean_x = mean(pull(Part1Question1, x))
mean_y = mean(pull(Part1Question1, y))
mean_z = mean(pull(Part1Question1, z))
mean_a = mean(pull(Part1Question1, a))

# Question: why the logical vector returned a mean value? It seems like R took FALSE as 0 and then TRUE as 1.
# Question: If this is OK to say yes, there is a value returned in the assignment?

# Now use the as.numeric function.
# Show the chuck but not the output.

# Question: Is this for all of above or is this only for this as.numeric part?
# If this is for all code chuck in Part 1, then change the beginning of the code chuck into:
 # {r results = HIDE part_1_of_Question_1}
 # Question: How do I keep both the name of the code chuck and the command together?
 # Question: What if I want to only hide the result of as.numeric part?

numeric_y = as.numeric(pull(Part1Question1, y)) 
numeric_z = as.numeric(pull(Part1Question1, z))
numeric_a = as.numeric(pull(Part1Question1, a))

```

For the mean value finding part:
a and y returned mean values.
z and a did not return a mean value since z and a are not numeric.

For the as.numeric part:
All y, z and a values are converted into numeric vectors and it seemed like y are fine with this conversion; however, there are NA values introduced in the dataset forcefully.
Yes, this does explain what happened when we are trying for mean function for the last part. R can't execuate mean function properly unless we have numerical values in the dataset.

#### Now Part 2 of Question 1:
##### * convert the logical vector to numeric, and multiply the random sample by the result
##### * convert the logical vector to a factor, and multiply the random sample by the result
##### * convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result


```{r}
# Here I have a error with {r results = hide}:
 ## Error in eval(x, envir = envir): object "hide" not found Calls: <Anonymous> ... process_group.block -> call_block -> eval_lang -> eval -> eval Execution halted

numeric_y_1 = numeric_y * pull(Part1Question1, x)
    # Question: What do the question mean by random sample by the result?
factor_y = as.factor(pull(Part1Question1, y))
####### ATTENTION #########
factor_y_1 = factor_y * pull(Part1Question1, x)
###########################
# Question: Here it said that * is not meaningful for factors, what do I do about this? Or do I leave this as it is?
numeric_y_2 = as.numeric(factor_y_1)
numeric_y_3 = numeric_y_2 * pull(Part1Question1, x)

```

# Problem 2

#### Create a data frame comprised of:
##### * x: a random sample of size 500 from a standard Normal distribution
##### * y: a random sample of size 500 from a standard Normal distribution
##### * A logical vector indicating whether x + y > 1
##### * A numeric vector created by coercing the above logical vector
##### * A factor vector created by coercing the above logical vector

```{r}

set.seed(10)
# Question: Do I need another set.seed()?
# If I have a set.seed() here will it make x and y the same outputs?

Question2 = tibble(
  x = rnorm(500),
  y = rnorm(500),
  z = x + y > 1,
  a = as.numeric(z),
  b = as.factor(z))

# Dataframe created.

```

* The size of the dataset are `r nrow(pull(Question2))` rows and `r ncol(pull(Question2))` columns.

``` {r}
# Question: Am I using this wrongly so this does not came out the way I wanted? How do I do this?
```

* The mean of x is `r mean(pull(Question2, x))`.

* The medium of x is `r median(pull(Question2, x))`.

* The standard deviation of x is `r sd(pull(Question2, x))`.

* The proportion of cases for which x + y > 1 is `r `

```{r}
# Question: How do I find proportion?
# Try for scatterplot tomorrow.
```

